Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-04 tex/test-WW-type-00s-PS.tex
alexei

WW-relations for FFs are actually not needed: in Eqs.~%
(\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-2})
either twist-2 FFs $D_1^a$, $H_1^{\perp a}$ enter or tilde FFs, as a consequence 
of how the azimuthal angles are defined \cite{Bacchetta:2006tn}. 
For completeness we quote the WW-type approximations for FFs
\cite{Bacchetta:2006tn}
\begin{subequations}\ba
	E(z,\pperp^2)      &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-1}\\
	G^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-2}\\
	D^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}
	& \hspace{11mm}z\,D_1(z,\pperp)\,, \label{Eq:WW-type-FF-3}\\
	H(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 
	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp)\,. \label{Eq:WW-type-FF-4}
\ea\end{subequations}
Having introduced the WW- and WW-type approximations, we will review
in the following what is currently known from theory and experiment 
about our approximations.

@@

We have seen that the following 6 TMDs and 2 FFs provide a basis 
(Sec.~\ref{Sec-3:WW}) and allow us to express all SIDIS structure 
functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation})  
in WW-type approximation: 
\be\label{Eq:basis}
   \mbox{basis: \ \ } 
   f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a};
   \; D_1^a, \; H_1^{\perp a} \, .
\ee
Phenomenological information is available for all basis functions at 
least to some extent. 
In Fig.~\ref{basis} we present plots of the basis functions, and refer
to App.~\ref{App:basis} for details.
The four functions $f_1^a, \; g_1^a, \; h_1^a,\; D_1^a$  
are related to twist-2 collinear functions. All collinear functions are calculated at $Q^2 = 2.4$ (GeV$^2$). Collinear $f_1(x)$ are from Ref.~\cite{Martin:2009iq},  $g_1(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1(z)$ are from Ref. ~\cite{deFlorian:2007aj}.The other four 
$f_{1T}^{\perp a},  \;h_1^{\perp a},\; H_1^{\perp a} \,$  
have no collinear counterparts, and we consider their (1)-moments, while 
for $ h_{1T}^{\perp a}$  we consider the (2)-moment, see App.~\ref{App:basis} for details.

@@

The structure function $F_{UU}$ needed for our analysis reads
\begin{subequations}\ba
	F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)\,{\cal G}(\Phperp)\,, 
	\label{Eq:FUU-Phperp}\\
	F_{UU}(x,z) \equiv \int d^2 \Phperp \, F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)  \, ,
	\label{Eq:FUU}
\ea\end{subequations}
where we introduce the notation ${\cal G}(\Phperp)$, which is defined as
\be\label{Eq:def-Gaussian-lambda}
	{\cal G}(\Phperp) = \frac{\exp(-\Phperp^2/\lambda)}{\pi\,\lambda}
	\, , \;\;\; 
	\lambda = z^2\,\la\kperp^2\ra_{f_1} + \la\pperp^2\ra_{D_1} \,,
\ee
with the understanding that the convenient abbreviation $\lambda$ is expressed 
in terms of the Gaussian widths of the {\it preceding} TMD and FF. Notice 
that ${\cal G}(\Phperp)\equiv {\cal G}(x,z,\Phperp)$ and that in general
${\cal G}(\Phperp)$ appears under the flavor sum due to a possible 
flavor-dependence of the involved Gaussian widths.
The normalization $\int d^2\Phperp \,{\cal G}(\Phperp)=1$ 
correctly connects the structure function $F_{UU}(x,z,\Phperp)$ 
in (\ref{Eq:FUU-Phperp}) with its $\Phperp$-integrated counterpart
(\ref{Eq:FUU}). In our effective description this is step is trivial. In 
QCD the connection of TMDs to PDFs is far more subtle \cite{Collins:2016hqq}.
Fig.~\ref{FUU-show-pT-dependence} illustrates how the Gauss Ansatz
describes selected SIDIS data. In Fig.~\ref{FUU-show-pT-dependence} (b) we plot HERMES multiplicity \cite{Airapetian:2012ki}
\be
M_n^h(x,z,\Phperp)  \equiv 2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
\ee
at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$ for $\pi^+$ production on the proton target.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.3\textwidth]{\FigPath/Fig02a-JLab-ratio-pT-v5.pdf}  (a)
\includegraphics[width=0.37\textwidth]{\FigPath/hermes_pip.pdf} (b)
\caption{\label{FUU-show-pT-dependence}
Examples of the description of transverse momenta of hadrons in 
unpolarized SIDIS. 
(a) Differential cross section at $\la Q^2\ra=2.37\,{\rm GeV}^2$,
$\la x\ra  =0.24$, $\la z\ra  =0.30$ measured at JLab with a 5.75 GeV 
beam \cite{Osipenko:2008aa}. Theoretical curve from Gauss model 
following Ref.~\cite{Schweitzer:2010tt}.
(b) Example for HERMES multiplicities at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering 
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pip}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pi0}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pim}  
\caption{\label{jlab_ALL} 
	$p_2 A_{LL}$ asymmetry compared with Jefferson Lab experimental 
	results Ref.~\cite{Avakian:2010ae} for $\pi^+$ (left panel) and 
	$\pi^-$ (right panel). Solid lines are computations with mean 
	values of kinematic variables  $\langle x \rangle = 0.25$, 
	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.7$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_f1t_jlab}.

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
\caption{\label{aut_f1t_jlab} $A_{UT}^{\sin(\phi_h-\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1_jlab}.

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
\caption{\label{aut_h1_jlab} $A_{UT}^{\sin(\phi_h+\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The structure function $F_{UU}^{\cos(2\phi_h)}$ reads
\begin{subequations}\ba
	F_{UU}^{\cos(2\phi_h)}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,h_{1}^{\perp (1) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(2)}_{\rm AB}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{UU}^{\cos2\phi_h}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1}^{\perp(1) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(2)}_{\rm AB}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_1^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(2)}_{\rm AB}=\red{4}M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
see App.~\ref{App:convol-details}.

Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
Jefferson Lab 12 GeV are plotted in Fig.~\ref{auu_cos2phi_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
\caption{\label{auu_cos2phi_jlab} $A_{UU}^{\cos(2\phi_h)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints. I would also
skip the Cahn effect for simplicity, and add a comment of the following
kind:)}

In the (to be updated) Fig.~\ref{auu_cos2phi_jlab} we plot only the
Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
the data accurately. In fact, it is suspected that this observable receives 
a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
term of higher twist character of the type $\la\Phperp^2\ra/Q^2$ which 
is not negligible in fixed target experiments \cite{Schweitzer:2010tt}. 
This contribution was estimated and corrected for in the phenomenological 
works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} which was of
importance to obtain a picture of the Boer-Mulders function undistorted 
from Cahn effect. The point is that this substantial twist-4 contamination 
can be estimated phenomenologically, even though there is no rigorous 
theoretical basis for the description of such power-suppressed terms. 
In this work we consistently neglect power-suppressed contributions of 
order $1/Q^2$, and do so also in Fig.~\ref{auu_cos2phi_jlab}. 
Nevertheless we of course use the parametrizations of 
\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} offering
the best currently available parametrizations for $h_1^{\perp}$
which were corrected for Cahn effect as good as it is possible at
the current stage of art. It is unknown whether other asymmetries
could be similarly effected by such type of power-corrections.
This is an important point to be kept in mind as the lesson 
from Fig.~\ref{auu_cos2phi_jlab} shows.

@@

The structure function $F_{UT}^{\sin(3\phi_h-\phi_S)}$ reads
\begin{subequations}\ba
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\Phperp)
	&=& x \sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(3)}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!3}\,
	{ \cal G}(\Phperp) \, , \;\;\;\;
	\label{eq:asymmetry_aut_h1tp} \\
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(3)}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!\red{3}}\,,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3\sqrt{\pi} \,M_N^2m_h$,
see App.~\ref{App:convol-details}.

Asymmetries $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1tp_jlab}.

\PS{\bf (We should plot here COMPASS data for illustrative purposes. 
I would propose to add a comment of the type:)}

>>>>

WW-relations for FFs are actually not needed: in Eqs.~%
(\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-2})
either twist-2 FFs $D_1^a$, $H_1^{\perp a}$ enter or tilde FFs, as a consequence 
of how the azimuthal angles are defined \cite{Bacchetta:2006tn}. 
For completeness we quote the WW-type approximations for FFs
\cite{Bacchetta:2006tn}
\begin{subequations}\ba
	E(z,\pperp^2)      &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-1}\\
	G^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-2}\\
	D^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}
	& \hspace{11mm}z\,D_1(z,\pperp^2)\,, \label{Eq:WW-type-FF-3}\\
	H(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 
	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp^2)\,. \label{Eq:WW-type-FF-4}
\ea\end{subequations}
Having introduced the WW- and WW-type approximations, we will review
in the following what is currently known from theory and experiment 
about our approximations.

@@

We have seen that the following 6 TMDs and 2 FFs provide a basis 
(Sec.~\ref{Sec-3:WW}) and allow us to express all SIDIS structure 
functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation})  
in WW-type approximation: 
\be\label{Eq:basis}
   \mbox{basis: \ \ } 
   f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a};
   \; D_1^a, \; H_1^{\perp a} \, .
\ee
Phenomenological information is available for all basis functions at 
least to some extent. 
In Fig.~\ref{basis} we present plots of the basis functions, and refer
to App.~\ref{App:basis} for details.
The four functions $f_1^a, \; g_1^a, \; h_1^a,\; D_1^a$  
are related to twist-2 collinear functions. All collinear functions are calculated at $Q^2 = 2.4$ (GeV$^2$). Collinear $f_1(x)$ are from Ref.~\cite{Martin:2009iq},  $g_1(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1(z)$ are from Ref. ~\cite{deFlorian:2007aj}.The other four 
$f_{1T}^{\perp a},  \;h_1^{\perp a},\; H_1^{\perp a} \,$  
have no collinear counterparts, and we consider their (1)-moments, while 
for $ h_{1T}^{\perp a}$  we consider the (2)-moment,
such that parametrizations of TMD functions read
\begin{subequations}\ba
f^a_1(x,\kperp^2) &=& f^a_1(x)\;
    \frac{e^{-\kperp^2/\avkperp_{f_1}}}{\pi\avkperp_{f_1}} \, ,\\
    D^a_1(z,\pperp^2) &=& D_1^a(z)\,
    \frac{e^{-\pperp^2/\avpperp_{D_1}}}{\pi\avpperp_{D_1}} \, ,\\
g^a_1(x,\kperp^2) &=& g^a_1(x)\;
    \frac{e^{-\kperp^2/\avkperp_{g_1}}}{\pi\avkperp_{g_1}} \, ,\\    
f_{1T}^{\perp q}(x,\kperp^2) &=&  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}} \, ,\\
h_{1}^{q} (x, \kperp^2) &=&h_{1}^{q} (x)  \frac{e^{-{\kperp^2}/{\avkperp_{h_1} }}}{\pi \avkperp_{h_1}}\, ,\\
H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
h_{1}^{\perp q}(x,\kperp^2) &=&  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\, ,\\
h_{1T}^{\perp q}(x,\kperp^2) &=&  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}} \, ,
\ea\end{subequations}
see App.~\ref{App:basis} for details.

@@

The structure function $F_{UU}$ needed for our analysis reads
\begin{subequations}\ba
	F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)\,{\cal G}(\Phperp)\,, 
	\label{Eq:FUU-Phperp}\\
	F_{UU}(x,z) \equiv \int d^2 \Phperp \, F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)  \, ,
	\label{Eq:FUU}
\ea\end{subequations}
where we introduce the notation ${\cal G}(\Phperp)$, which is defined as
\be\label{Eq:def-Gaussian-lambda}
	{\cal G}(\Phperp) = \frac{\exp(-\Phperp^2/\lambda)}{\pi\,\lambda}
	\, , \;\;\; 
	\lambda = z^2\,\la\kperp^2\ra_{f_1} + \la\pperp^2\ra_{D_1} \,,
\ee
with the understanding that the convenient abbreviation $\lambda$ is expressed 
in terms of the Gaussian widths of the {\it preceding} TMD and FF. Notice 
that ${\cal G}(\Phperp)\equiv {\cal G}(x,z,\Phperp)$ and that in general
${\cal G}(\Phperp)$ appears under the flavor sum due to a possible 
flavor-dependence of the involved Gaussian widths.
The normalization $\int d^2\Phperp \,{\cal G}(\Phperp)=1$ 
correctly connects the structure function $F_{UU}(x,z,\Phperp)$ 
in (\ref{Eq:FUU-Phperp}) with its $\Phperp$-integrated counterpart
(\ref{Eq:FUU}). In our effective description this is step is trivial. In 
QCD the connection of TMDs to PDFs is far more subtle \cite{Collins:2016hqq}.
Fig.~\ref{FUU-show-pT-dependence} illustrates how the Gauss Ansatz
describes selected SIDIS data. In Fig.~\ref{FUU-show-pT-dependence} (b) we plot HERMES multiplicity \cite{Airapetian:2012ki}
\be
M_n^h(x,z,\Phperp)  \equiv 2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
\ee
at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$ for $\pi^+$ production on the proton target.
In Fig.~\ref{FUU-show-pT-dependence} (c) we plot COMPASS multiplicity \cite{Aghasyan:2017ctw}
\be
n^h(x,z,\Phperp)  \equiv \pi \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
\ee
at $\la Q^2\ra=20\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.2$ for $h^+$ production on the deuterium target.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.3\textwidth]{\FigPath/Fig02a-JLab-ratio-pT-v5.pdf}  (a)
\includegraphics[width=0.37\textwidth]{\FigPath/hermes_pip.pdf} (b)
\includegraphics[width=0.37\textwidth]{\FigPath/compass_hp.pdf} (c)
\caption{\label{FUU-show-pT-dependence}
Examples of the description of transverse momenta of hadrons in 
unpolarized SIDIS. 
(a) Differential cross section at $\la Q^2\ra=2.37\,{\rm GeV}^2$,
$\la x\ra  =0.24$, $\la z\ra  =0.30$ measured at JLab with a 5.75 GeV 
beam \cite{Osipenko:2008aa}. Theoretical curve from Gauss model 
following Ref.~\cite{Schweitzer:2010tt}.
(b) Example for HERMES multiplicities \cite{Airapetian:2012ki} at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$.
(b) Example for COMPASS multiplicities \cite{Aghasyan:2017ctw} at $\la Q^2\ra=20\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.2$.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering 
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pip}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pi0}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pim}  
\caption{\label{jlab_ALL} 
	$A_{LL,\la y\ra}$ asymmetry compared with Jefferson Lab experimental 
	results Ref.~\cite{Avakian:2010ae} for $\pi^+$ (left panel) and 
	$\pi^-$ (right panel). Solid lines are computations with mean 
	values of kinematic variables  $\langle x \rangle = 0.25$, 
	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.7$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
and comparison to HERMES data \cite{Airapetian:2009ae} are plotted in Fig.~\ref{aut_f1t_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
\caption{\label{aut_f1t_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h-\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2011gs} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
and comparison to HERMES data \cite{Airapetian:2010ds} are plotted in Fig.~\ref{aut_h1_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
\caption{\label{aut_h1_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h+\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2013vqa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The structure function $F_{UU}^{\cos(2\phi_h)}$ reads
\begin{subequations}\ba
	F_{UU}^{\cos(2\phi_h)}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,h_{1}^{\perp (1) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(2)}_{\rm AB}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{UU}^{\cos2\phi_h}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1}^{\perp(1) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(2)}_{\rm AB}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_1^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(2)}_{\rm AB}=4M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
see App.~\ref{App:convol-details}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
\caption{\label{auu_cos2phi_jlab} Comparison of calculation of $A_{UU}^{\cos(2\phi_h)}$  using fit results of Ref.~\cite{Barone:2015ksa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Giordano:2009hi}.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
HERMES are plotted in Fig.~\ref{auu_cos2phi_jlab}.
In the Fig.~\ref{auu_cos2phi_jlab} we plot only the
Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
the data accurately. In fact, it is suspected that this observable receives 
a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
term of higher twist character of the type $\la\Phperp^2\ra/Q^2$ which 
is not negligible in fixed target experiments \cite{Schweitzer:2010tt}. 
This contribution was estimated and corrected for in the phenomenological 
works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} which was of
importance to obtain a picture of the Boer-Mulders function undistorted 
from Cahn effect. The point is that this substantial twist-4 contamination 
can be estimated phenomenologically, even though there is no rigorous 
theoretical basis for the description of such power-suppressed terms. 
In this work we consistently neglect power-suppressed contributions of 
order $1/Q^2$, and do so also in Fig.~\ref{auu_cos2phi_jlab}. 
Nevertheless we of course use the parametrizations of 
\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} offering
the best currently available parametrizations for $h_1^{\perp}$
which were corrected for Cahn effect as good as it is possible at
the current stage of art. It is unknown whether other asymmetries
could be similarly effected by such type of power-corrections.
This is an important point to be kept in mind as the lesson 
from Fig.~\ref{auu_cos2phi_jlab} shows.

@@

The structure function $F_{UT}^{\sin(3\phi_h-\phi_S)}$ reads
\begin{subequations}\ba
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\Phperp)
	&=& x \sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(3)}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!3}\,
	{ \cal G}(\Phperp) \, , \;\;\;\;
	\label{eq:asymmetry_aut_h1tp} \\
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(3)}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{3}\,,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3/2\sqrt{\pi} \,M_N^2m_h$,
see App.~\ref{App:convol-details}.
